Modelling of electron acceleration in relativistic supernovae

### 2019-05-21 papers/Physica2019/Romansky_Physica2019.tex
paper

>>>>

We tested setup with a longer transverse size of the simulation region, corresponding to approximately $40$ gyroradii of the upstream protons, with the magnetic turbulence energy fraction 90\%. The spectrum of the accelerated electrons has no qualitative differences from the setup with a smaller transverse size since the non-thermal part of the distribution function survives.  We also studied the effect of the proton to electron  mass ratio within a setup with  $\frac{m_p}{m_e} = 50$. The spectrum obtained has a similar dependence on the turbulence energy fraction and scale. It is shown in Figure \ref{electrons_mass} that the electron spectrum in the higher mass ratio setup is just shifted to the higher Lorentz-factors, while  the fraction of the energy in accelerated electrons  $\epsilon_e = 2.5\cdot10^{-3}$ is almost the same as in the case with $\frac{m_p}{m_e} = 25$.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{fig/electrons_mass.eps} 
	\caption{Distribution of electrons in the relativistic shock wave with different mass relation, turbulence energy fraction is 90\%.}
	\label{electrons_mass}
\end{figure}
